%  ========================================================================
%  Copyright (c) 1995-2012 The University of Washington
%
%  Licensed under the Apache License, Version 2.0 (the "License");
%  you may not use this file except in compliance with the License.
%  You may obtain a copy of the License at
%
%      http://www.apache.org/licenses/LICENSE-2.0
%
%  Unless required by applicable law or agreed to in writing, software
%  distributed under the License is distributed on an "AS IS" BASIS,
%  WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
%  See the License for the specific language governing permissions and
%  limitations under the License.
%  ========================================================================
%

% Documentation for UW thesis document style for LaTeX
% by Jim Fox
% fox@washington.edu
%
%    Revised for version 2012/06/19 of uwthesis.cls
%
%    This document is contained in a single file ONLY because
%    I wanted to be able to distribute it easily.  A real thesis ought
%    to be contained on many files (e.g., one for each chapter, at least).
%
%    To help you identify the files and sections in this large file
%    I use the string '==========' to identify new files.
%
%    To help you ignore the unusual things I do with this sample document
%    I try to use the notation
%       
%    % --- sample stuff only -----
%    special stuff for my document, but you don't need it in your thesis
%    % --- end-of-sample-stuff ---


%    Printed in twoside style now that that's allowed
%

 % TODO: 11pt or 12?
\documentclass [12pt, oneside] {uwthesis}[2012/06/19]
 
%
% The following line would print the thesis in a postscript font 

% \usepackage{natbib}
% \def\bibpreamble{\protect\addcontentsline{toc}{chapter}{Bibliography}}

\setcounter{tocdepth}{1}  % Print the chapter and sections to the toc
 

% ==========   Local defs and mods
%

% --- sample stuff only -----
% These format the sample code in this document

\usepackage{alltt}  % 
\newenvironment{demo}
  {\begin{alltt}\leftskip3em
     \def\\{\ttfamily\char`\\}%
     \def\{{\ttfamily\char`\{}%
     \def\}{\ttfamily\char`\}}}
  {\end{alltt}}
 
% metafont font.  If logo not available, use the second form
%
% \font\mffont=logosl10 scaled\magstep1
\let\mffont=\sf
% --- end-of-sample-stuff ---
 
% Math stuff
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{float}
\usepackage{tabularx}
\usepackage{multirow}

\setlength{\intextsep}{5pt}           % Controls spacing around float environments

\begin{document}
 
% ==========   Preliminary pages
%
% ( revised 2012 for electronic submission )
%

\prelimpages
 
%
% ----- copyright and title pages
%
\Title{Programmable System for Laser Control of Trapped-Ion Experiments}
\Author{Haochen Yu}
\Year{2025}
\Program{Electrical and Computer Engineering  }

\Chair{Scott Hauck}{}{Department of Electrical and Computer Engineering}
\Signature{Sara Mouradian }


\copyrightpage

% \titlepage  

% --- sample stuff only -----
% unusual footnote not found in a real thesis
% You just use the \titlepage as commented out above

{\Degreetext{A thesis\\
  submitted in partial fulfillment of the\\ requirements for the degree of}
 \let\footnoterule\relax
 \titlepage
 }
\setcounter{footnote}{0}

% --- end-of-sample-stuff ---
 
%
% ----- signature and quoteslip are gone
%

%
% ----- abstract
%


\setcounter{page}{-1}
\abstract{%
% TODO
Modern quantum computing experiments demand exceptional precision, especially when controlling laser pulses for trapped-ion systems. Recent optical breakthroughs now pack dozens of channels onto a single chip, enabling efficient multichannel laser control. However, the supporting electronics often lack the necessary timing accuracy and flexibility. This shortfall can hinder progress and frustrate researchers.

This thesis presents an FPGA-based laser control system on a Xilinx Zynq platform. A key module generates precise pulse waveforms and integrates into a system that delivers 32 pulsed and 32 static voltage signals. By leveraging dual-port block memories, state machines, and high-speed interfaces, the system achieves sub-microsecond timing with low resource usage. Simulation and board testing confirm accurate pulse generation while highlighting opportunities for enhanced precision and improved error handling. Overall, this work offers a reliable, scalable, and cost-effective solution for advanced FPGA applications in quantum control.
}
 
%
% ----- contents & etc.
%
\tableofcontents
\listoffigures
\listoftables 
 
%
% ----- acknowledgments
%
\acknowledgments{% \vskip2pc
  % {\narrower\noindent

I extend my deepest gratitude to everyone who has supported me on this journey. I am especially thankful to my advisor, Professor Scott Hauck, whose guidance and unwavering support have been indispensable. Working in his laboratory provided me with incredible opportunities and invaluable resources that enriched my personal, academic, and professional growth.

I also appreciate Professor Sara Mouradian, a valued member of my thesis committee, has been a driving force behind this project. Her strategic vision and deep understanding of its foundations have consistently propelled innovation and advanced its potential.

A sincere thank the ACME lab team for their invaluable help during the process. Special thanks to Geoffrey Jones for initiating the design. His insights and technical effort have shaped every corner of the system.

I truly appreciate the support of my friends and family. I am thank to Buke Hu from QT3 Laboratory for providing essential publications on the project’s application, and to ACME alumni Jeffery Xu for his technical guidance during the design phase. Lastly, I owe my deepest appreciation to my mother, Dr. Li Yang, whose constant encouragement has been a cornerstone of my journey.
  % \par}
}
 
 
 
%
% ==========      Text pages
%

\textpages


\input{chapters/intro}
\input{chapters/bg}
\input{chapters/block_arch}
\input{chapters/spec}
\input{chapters/sys}
\input{chapters/result}
\input{chapters/discussion}
\input{chapters/conclusion}

%
% ==========   Bibliography
%
\nocite{*}   % include everything in the uwthesis.bib file
\bibliographystyle{plain}
\bibliography{uwthesis}


\end{document}
